---
title: "Determining the repeatability of turtle behaviour"
output:
  word_document: default
  html_document: default
  pdf_document: default
---
```{r setup, include=FALSE} 
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
```
R code to calculate the among-individual repeatabilty of the turtles behaviours ((handling reaction (Aggression), shell emergence time (Shell), time of initial movement (Start), total time spent moving (Move)). 

# Packages 
```{r message=FALSE}
library(rptR)
library(ggplot2)
library(car)
library(multcomp)
library(lmtest)
library(lme4)
library(Hmisc)
library(writexl)
library(dplyr)
library(lmerTest)
library(optimx)
library(PerformanceAnalytics)
library(effects)
library(ggeffects) 
library(splines)
library(glmtoolbox)
library(afex)
library(nloptr)
library(dfoptim)
library(psych)
library(ordinal)
library(ggpubr)
```

# Upload the dataset to use
```{r message=FALSE}
Behaviour<-read.csv("C:/Users/sebas/Desktop/Masters Work/Masters Work/Stats/Bin.Shell.600/Combined Repeatability Dataset.600.csv")
```

# Preparing data
```{r}
Behaviour$Shell <- as.numeric(Behaviour$Shell)
Behaviour$Aggression <- as.numeric(Behaviour$Aggression)
Behaviour$Start <- as.numeric(Behaviour$Start)
Behaviour$Move <- as.numeric(Behaviour$Move)
Behaviour$BIN.Shell <- as.numeric(Behaviour$BIN.Shell)
```

# Plot data
I am doing this step to make sure I use the right data distribution in my models.
```{r}
ggplot(Behaviour, aes(x=Start)) + geom_histogram()
ggplot(Behaviour, aes(x=Move)) + geom_histogram()
ggplot(Behaviour, aes(x=Aggression)) + geom_histogram()
ggplot(Behaviour, aes(x=Shell)) + geom_histogram()
```
Time of initial movement (Start) has a skewed distribution so I will try log transforming it. 

# Transform inital time of movement
```{r}
Behaviour$log.Start <- log(Behaviour$Start + 1)
```

# Prepare log(x+1) transformed version of initial time of movement (log.Start)
```{r}
Behaviour$log.Start <- as.numeric(Behaviour$log.Start)
```

# Plot log(x+1) transformed version of initial time of movement
```{r}
ggplot(Behaviour, aes(x=log.Start)) + geom_histogram()
```
The log(x+1) transformed version of time of initial movement is still somewhat skewed, so I will run my analysis on both versions for comparison. Shell emergence time (Shell) is also skewed, so I will plot the binary version of it.

# Plot binary shell emergence time (BIN.Shell)
```{r}
ggplot(Behaviour, aes(x=BIN.Shell)) + geom_histogram()
```

# Calculation of sources of variance and repeatability estimates
For my study I set the bootstrap value to 1000, but for this R Code, I set the value to 10 to reduce the calculation time for some of the models, especially for the adjusted estimations.This does not affect the value of the repeatability estimates or p-values, but it does affect the values for the standard errors and 95% confidence intervals

## Time of initial movement (Start)
### Unadjusted
For the unadjusted estimations, I only included turtle ID (Code) as a random effect.

#### Repeatability
```{r echo=T, results='hide'}
rep.Start <- rpt(Start ~ (1 | Code), grname = "Code", data = Behaviour, datatype = "Gaussian", nboot = 10, npermut = 0)
```
##### Analysis
```{r}
summary(rep.Start)
plot(rep.Start)
plot(rep.Start$mod)
qqnorm(resid(rep.Start$mod))
print(rep.Start)
```
### Adjusted
For the adjusted estimations, I also included turtle sex (Sex) and day of testing (Day) as fixed effects, and site identity (Site) as a random effect.

#### Repeatability
```{r echo=T, results='hide'}
rep.fix.Start <- rpt(Start ~ Day + Sex + (1 | Code) + (1 | Site), grname = "Code", data = Behaviour, datatype = "Gaussian", 
                            nboot = 10, npermut = 0)
```

##### Analysis
```{r}
summary(rep.fix.Start)
plot(rep.fix.Start)
plot(rep.fix.Start$mod)
qqnorm(resid(rep.fix.Start$mod))
print(rep.fix.Start)
```

## Log(x+1) transformed version ot time of initial movement (log.Start)
### Unadjusted
For the unadjusted estimations, I only included turtle ID (Code) as a random effect.

#### Repeatability
```{r echo=T, results='hide'}
rep.log.Start <- rpt(log.Start ~ (1 | Code), grname = "Code", data = Behaviour, datatype = "Gaussian", nboot = 10, npermut = 0)
```

##### Analysis
```{r}
summary(rep.log.Start)
plot(rep.log.Start)
plot(rep.log.Start$mod)
qqnorm(resid(rep.log.Start$mod))
print(rep.log.Start)
```

### Adjusted
For the adjusted estimations, I also included turtle sex (Sex) and day of testing (Day) as fixed effects, and site identity (Site) as a random effect.

#### Repeatability
```{r echo=T, results='hide'}
rep.fix.log.Start <- rpt(log.Start ~ Day + Sex + (1 | Code) + (1 | Site), grname = "Code", data = Behaviour, datatype = "Gaussian", 
                            nboot = 10, npermut = 0)
```

##### Analysis
```{r}
summary(rep.fix.log.Start)
plot(rep.fix.log.Start)
plot(rep.fix.log.Start$mod)
qqnorm(resid(rep.fix.log.Start$mod))
print(rep.fix.log.Start)
```

## Total time spent moving (Move)
### Unadjusted
For the unadjusted estimations, I only include turtle ID (Code) as a random effect.

#### Repeatability
```{r echo=T, results='hide'}
rep.Move <- rpt(Move ~ (1 | Code), grname = "Code", data = Behaviour, datatype = "Gaussian", nboot = 10, npermut = 0)
```

##### Analysis
```{r}
summary(rep.Move)
plot(rep.Move)
plot(rep.Move$mod)
qqnorm(resid(rep.Move$mod))
print(rep.Move)
```

### Adjusted
For the adjusted estimations, I also included turtle sex (Sex) and day of testing (Day) as fixed effects, and site identity (Site) as a random effect.

#### Repeatability
```{r echo=T, results='hide'}
rep.fix.Move <- rpt(Move ~ Day + Sex + (1 | Code) + (1 | Site), grname = "Code", data = Behaviour, datatype = "Gaussian", 
                       nboot = 10, npermut = 0)
```

##### Analysis 
```{r}
summary(rep.fix.Move)
plot(rep.fix.Move)
plot(rep.fix.Move$mod)
qqnorm(resid(rep.fix.Move$mod))
print(rep.fix.Move)
```

## Handling reaction (Aggression)
### Unadjusted
For the unadjusted estimations, I only included turtle ID (Code) as a random effect.

#### Repeatability
```{r echo=T, results='hide'}
rep.Aggression <- rpt(Aggression ~ (1 | Code), grname = "Code", data = Behaviour, datatype = "Gaussian", nboot = 10, npermut = 0)
```

##### Analysis
```{r}
summary(rep.Aggression)
plot(rep.Aggression)
plot(rep.Aggression$mod)
qqnorm(resid(rep.Aggression$mod))
print(rep.Aggression)
```

### Adjusted
For the adjusted estimations, I also included turtle sex (Sex) and day of testing (Day) as fixed effects, and site identity (Site) as a random effect.

#### Repeatability 
```{r echo=T, results='hide'}
rep.fix.Aggression <- rpt(Aggression ~ Day + Sex + (1 | Site) + (1 | Code), grname = "Code", data = Behaviour, datatype = "Gaussian", 
                            nboot = 10, npermut = 0)
```

##### Analysis
```{r}
summary(rep.fix.Aggression)
plot(rep.fix.Aggression)
plot(rep.fix.Aggression$mod)
qqnorm(resid(rep.fix.Aggression$mod))
print(rep.fix.Aggression)
```

## Shell emergence time (binary) (BIN.Shell)
### Unadjusted
For the unadjusted estimations, I only included turtle ID (Code) as a random effect.

#### Repeatability
```{r echo=T, results='hide'}
rep.Bin.Shell <- rpt(BIN.Shell ~ (1 | Code), grname = "Code", data = Behaviour, datatype = "Binary", nboot = 10, npermut = 0)
```

##### Analysis
```{r}
summary(rep.Bin.Shell)
plot(rep.Bin.Shell)
plot(rep.Bin.Shell$mod)
qqnorm(resid(rep.Bin.Shell$mod))
print(rep.Bin.Shell)
```

### Adjusted
For the adjusted estimations, I also included turtle sex (Sex) and day of testing (Day) as fixed effects, and site identity (Site) as a random effect.

#### Repeatability 
```{r echo=T, results='hide'}
rep.fix.Bin.Shell <- rpt(BIN.Shell ~ Day + Sex + (1 | Code) + (1 | Site), grname = "Code", data = Behaviour, datatype = "Binary", 
                            nboot = 10, npermut = 0)
```

##### Analysis
```{r}
summary(rep.fix.Bin.Shell)
plot(rep.fix.Bin.Shell)
plot(rep.fix.Bin.Shell$mod)
qqnorm(resid(rep.fix.Bin.Shell$mod))
print(rep.fix.Bin.Shell)
```