---
title: "Determination of the scale of maximum effect"
output:
  word_document: default
  pdf_document: default
  html_document: default
---
```{r setup, include=FALSE} 
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
```
R code to determine the distance at which each land class (forest/vegetation, urbanization, open water, wetland, and agriculture) had the maximum effect on the turtles behaviours (handling reaction (Aggression), shell emergence time (Shell), time of initial movement (Start), total time spent moving (Movement)).

## Packages
```{r message=FALSE}
library("plyr")
library("dplyr")
library("writexl")
library("rptR")
library("tidyverse")
library("blmeco")
library("PerformanceAnalytics")
library("Hmisc")
library("pspearman")
library("lme4")
```

## Upload the dataset to use
```{r}
cor<-read.csv("C:/Users/sebas/Desktop/Masters Work/Masters Work/Stats/Bin.Shell.600/Correlations 2022.600.csv")
```

## Function to linearize a correlation matrix
```{r}
flattenCorrMatrix <- function(cormat, pmat) {
  ut <- upper.tri(cormat)
  data.frame(
    row = rownames(cormat)[row(cormat)[ut]],
    column = rownames(cormat)[col(cormat)[ut]],
    cor  =(cormat)[ut],
    p = pmat[ut]
  )
}
```

## Preparing data
```{r}
cor$Aggression<- as.numeric(cor$Aggression)
cor$Shell <- as.numeric(cor$Shell)
cor$Start <- as.numeric(cor$Start)
cor$Movement <- as.numeric(cor$Movement)
```

## Plot data
I am doing this step to make sure I use the right data distribution for my models later on. If I do need to transform any of the data distributions, I will need to recalculate the distance at which each land cover class has a maximum impact on the transformed behaviour.
```{r message=FALSE}
ggplot(cor, aes(x=Aggression)) + geom_histogram()
ggplot(cor, aes(x=Shell)) + geom_histogram()
ggplot(cor, aes(x=Start)) + geom_histogram()
ggplot(cor, aes(x=Movement)) + geom_histogram()
```
Time of initial movement has a skewed distribution so I will plot a log transformed version of it. 

## Prepare log(x+1) transformed version of time of initial movement (log.Start)
```{r}
cor$log.Start <- as.numeric(cor$log.Start)
```

## Plot log(x+1) transformed version of time of initial movement
```{r}
ggplot(cor, aes(x=log.Start)) + geom_histogram()
```
The log transformed version of time of initial movement is still somewhat skewed, so I will run my analysis on both versions for comparison. Shell emergence time is also skewed, so I will plot the binary version of it.

## Prepare binary version of shell emergence time (Bin.Shell)
```{r}
cor$Bin.Shell <- as.numeric(cor$Bin.Shell)
```

## Plot binary version of shell emergence time data
```{r}
ggplot(cor, aes(x=Bin.Shell)) + geom_histogram()
```

## Correlations 
### Handling reactions (Aggression)
#### Creation of the dataset
I need to create a new dataset that excludes all turtles with no observations for handling reactions
```{r}
# deletion of the NA's
cor.agres <- cor[complete.cases(cor$Aggression),]

# deletion of the columns for shell emergence time (and binary version), total time spent moving, and time of initial movement (and log transformed version)

drop <- c("Shell","Bin.Shell","Movement","Start","log.Start")
cor.agres = cor.agres[,!(names(cor.agres) %in% drop)]
```

##### Pearson correlations between handling reactions and land cover for each buffer distance
```{r}
cor.pearson.agres <- rcorr(as.matrix(cor.agres[,3:53]), type="pearson")
```

##### Linearization of the correlation matrix
```{r}
table.cor.agres <- flattenCorrMatrix(cor.pearson.agres$r, cor.pearson.agres$P)
```

##### Save the table with the correlation in xlsx format.
```{r}
write_xlsx(table.cor.agres, "C:/Users/sebas/Desktop/Masters Work/Masters Work/Stats/New Stats/Land Cover Correlation/Buffer Correlation/2022/Buffer Correlation Rankings/1000m Buffer Rankings/cor.agres.xlsx")
```

##### Upload the dataset that contain only the correlations with handling reaction (delete all rows that don't have handling reaction). 

```{r}
#I deleted the rows in Microsoft Excel
cor.agres.final<-read.csv("C:/Users/sebas/Desktop/Masters Work/Masters Work/Stats/New Stats/Land Cover Correlation/Buffer Correlation/2022/Buffer Correlation Rankings/1000m Buffer Rankings/cor.agres.csv")
```

##### Graphics illustrating the correlations between handling reaction and landcover types at different buffer distances
```{r}
#Urban
ggplot(data=cor.agres.final, aes(x=buffer, y=cor.urban)) +
  geom_line() +
  geom_point() + 
  scale_x_continuous(breaks = c(100,200,300,400,500,600,700,800,900,1000))
#Forest/Vegatation
ggplot(data=cor.agres.final, aes(x=buffer, y=cor.for.veg)) +
  geom_line() +
  geom_point() + 
  scale_x_continuous(breaks = c(100,200,300,400,500,600,700,800,900,1000))
#Wetland
ggplot(data=cor.agres.final, aes(x=buffer, y=cor.wet)) +
  geom_line() +
  geom_point() + 
  scale_x_continuous(breaks = c(100,200,300,400,500,600,700,800,900,1000))
#Agriculture
ggplot(data=cor.agres.final, aes(x=buffer, y=cor.agri)) +
  geom_line() +
  geom_point() + 
  scale_x_continuous(breaks = c(100,200,300,400,500,600,700,800,900,1000))
#Water
ggplot(data=cor.agres.final, aes(x=buffer, y=cor.water)) +
  geom_line() +
  geom_point() + 
  scale_x_continuous(breaks = c(100,200,300,400,500,600,700,800,900,1000))
```

### Binary version of shell emergence time (Bin.Shell)
#### Creation of the dataset
I need to create a new dataset that excludes all turtles with no observation for shell emergence time (binary)
```{r}
cor.bin.sh <- cor[complete.cases(cor$Bin.Shell),]

# deletion of the columns for handling reaction, shell emergence, total time spent moving, and time of initial movement (and log transformed version)

drop <- c("Aggression", "Shell", "Movement", "Start", "log.Start")
cor.bin.sh = cor.bin.sh[,!(names(cor.bin.sh) %in% drop)]
```

##### Pearson correlations between shell emergence time (binary) and land cover for each buffer distance
```{r}
cor.pearson.bin.sh <- rcorr(as.matrix(cor.bin.sh[,3:53]), type="pearson")
```

##### Linearization of the correlation matrix
```{r}
table.cor.bin.sh <- flattenCorrMatrix(cor.pearson.bin.sh$r, cor.pearson.bin.sh$P)
```

##### Save the table with the correlation in xlsx format.
```{r}
write_xlsx(table.cor.bin.sh, "C:/Users/sebas/Desktop/Masters Work/Masters Work/Stats/Bin.Shell.600/cor.bin.sh.600.xlsx")
```

##### Upload the dataset that contain only the correlations with shell emergence time (binary) (delete all rows that don't have shell emergence time (binary)). 
```{r}
#I deleted the rows in Microsoft Excel
cor.bin.sh.final<-read.csv("C:/Users/sebas/Desktop/Masters Work/Masters Work/Stats/Bin.Shell.600/cor.bin.sh.600.csv")
```

##### Graphics illustrating the correlations between shell emergence time (binary) and landcover types at different buffer distances
```{r}
#Urban
ggplot(data=cor.bin.sh.final, aes(x=buffer, y=cor.urban)) +
  geom_line() +
  geom_point() + 
  scale_x_continuous(breaks = c(100,200,300,400,500,600,700,800,900,1000))
#Forest/Vegetation
ggplot(data=cor.bin.sh.final, aes(x=buffer, y=cor.for.veg)) +
  geom_line() +
  geom_point() + 
  scale_x_continuous(breaks = c(100,200,300,400,500,600,700,800,900,1000))
#Wetland
ggplot(data=cor.bin.sh.final, aes(x=buffer, y=cor.wet)) +
  geom_line() +
  geom_point() + 
  scale_x_continuous(breaks = c(100,200,300,400,500,600,700,800,900,1000))
#Agriculture
ggplot(data=cor.bin.sh.final, aes(x=buffer, y=cor.agri)) +
  geom_line() +
  geom_point() + 
  scale_x_continuous(breaks = c(100,200,300,400,500,600,700,800,900,1000))
#Water
ggplot(data=cor.bin.sh.final, aes(x=buffer, y=cor.water)) +
  geom_line() +
  geom_point() + 
  scale_x_continuous(breaks = c(100,200,300,400,500,600,700,800,900,1000))
```

### Time of initial movement (Start)
#### Creation of the dataset
I need to create a new dataset that excludes all turtles with no observation for time of initial movement
```{r}
cor.st <- cor[complete.cases(cor$Start),]

# deletion of the columns for handling reaction, shell emergence (and the binary version), total time spent moving, and the log transformed version of time of initial movement

drop <- c("Aggression", "Shell", "Bin.Shell", "Movement", "log.Start")
cor.st = cor.st[,!(names(cor.st) %in% drop)]
```

##### Pearson correlations between time of initial movement and land cover for each buffer distance 
```{r}
cor.pearson.st <- rcorr(as.matrix(cor.st[,3:53]), type="pearson")
```

##### Linearization of the correlation matrix
```{r}
table.cor.st <- flattenCorrMatrix(cor.pearson.st$r, cor.pearson.st$P)
```

##### Save the table with the correlation in xlsx format
```{r}
write_xlsx(table.cor.st, "C:/Users/sebas/Desktop/Masters Work/Masters Work/Stats/New Stats/Land Cover Correlation/Buffer Correlation/2022/Buffer Correlation Rankings/1000m Buffer Rankings/cor.st.xlsx")
```

##### Upload the dataset that contain only the correlations with time of initial movement (delete all rows that don't have time of initial movement). 
```{r}
#I deleted the rows in Microsoft Excel
cor.st.final<-read.csv("C:/Users/sebas/Desktop/Masters Work/Masters Work/Stats/New Stats/Land Cover Correlation/Buffer Correlation/2022/Buffer Correlation Rankings/1000m Buffer Rankings/cor.st.csv")
```

##### Graphics illustrating the correlations between time of initial movement and landcover types at different buffer distances
```{r}
#Urban
ggplot(data=cor.st.final, aes(x=buffer, y=cor.urban)) +
  geom_line() +
  geom_point() + 
  scale_x_continuous(breaks = c(100,200,300,400,500,600,700,800,900,1000))
#Forest/Vegetation
ggplot(data=cor.st.final, aes(x=buffer, y=cor.for.veg)) +
  geom_line() +
  geom_point() + 
  scale_x_continuous(breaks = c(100,200,300,400,500,600,700,800,900,1000))
#Wetland
ggplot(data=cor.st.final, aes(x=buffer, y=cor.wet)) +
  geom_line() +
  geom_point() + 
  scale_x_continuous(breaks = c(100,200,300,400,500,600,700,800,900,1000))
#Agriculture
ggplot(data=cor.st.final, aes(x=buffer, y=cor.agri)) +
  geom_line() +
  geom_point() + 
  scale_x_continuous(breaks = c(100,200,300,400,500,600,700,800,900,1000))
#Water
ggplot(data=cor.st.final, aes(x=buffer, y=cor.water)) +
  geom_line() +
  geom_point() + 
  scale_x_continuous(breaks = c(100,200,300,400,500,600,700,800,900,1000))
```

### Log(x+1) transformed version of time of initial movement (log.Start)
#### Creation of the dataset
I need to create a new dataset that excludes all turtles with no observation for the log(x+1) transformed version of time of initial movement
```{r}
cor.log.st <- cor[complete.cases(cor$log.Start),]

# deletion of the columns for handling reaction, shell emergence (and the binary version), total time spent moving, and the time of initial movement

drop <- c("Aggression", "Shell", "Bin.Shell", "Movement", "Start")
cor.log.st = cor.log.st[,!(names(cor.log.st) %in% drop)]
```

##### Pearson correlations between log(x+1) transformed version of time of initial movement and land cover for each buffer distance 
```{r}
cor.pearson.log.st <- rcorr(as.matrix(cor.log.st[,3:53]), type="pearson")
```

##### Linearization of the correlation matrix
```{r}
table.cor.log.st <- flattenCorrMatrix(cor.pearson.log.st$r, cor.pearson.log.st$P)
```

##### Save the table with the correlation in xlsx format
```{r}
write_xlsx(table.cor.log.st, "C:/Users/sebas/Desktop/Masters Work/Masters Work/Stats/New Stats/Land Cover Correlation/Buffer Correlation/2022/Buffer Correlation Rankings/1000m Buffer Rankings/cor.log.st.xlsx")
```

##### Upload the dataset that contain only the correlations with log(x+1) transformed version of time of initial movement (delete all rows that don't have log(x+1) transformed version of time of initial movement). 
```{r}
#I deleted the rows in Microsoft Excel
cor.log.st.final<-read.csv("C:/Users/sebas/Desktop/Masters Work/Masters Work/Stats/New Stats/Land Cover Correlation/Buffer Correlation/2022/Buffer Correlation Rankings/1000m Buffer Rankings/cor.log.st.csv")
```

##### Graphics illustrating the correlations between log(x+1) transformed version of time of initial movement and landcover types at different buffer distances
```{r}
#Urban
ggplot(data=cor.log.st.final, aes(x=buffer, y=cor.urban)) +
  geom_line() +
  geom_point() + 
  scale_x_continuous(breaks = c(100,200,300,400,500,600,700,800,900,1000))
#Forest/Vegetation
ggplot(data=cor.log.st.final, aes(x=buffer, y=cor.for.veg)) +
  geom_line() +
  geom_point() + 
  scale_x_continuous(breaks = c(100,200,300,400,500,600,700,800,900,1000))
#Wetland
ggplot(data=cor.log.st.final, aes(x=buffer, y=cor.wet)) +
  geom_line() +
  geom_point() + 
  scale_x_continuous(breaks = c(100,200,300,400,500,600,700,800,900,1000))
#Agriculture
ggplot(data=cor.log.st.final, aes(x=buffer, y=cor.agri)) +
  geom_line() +
  geom_point() + 
  scale_x_continuous(breaks = c(100,200,300,400,500,600,700,800,900,1000))
#Water
ggplot(data=cor.log.st.final, aes(x=buffer, y=cor.water)) +
  geom_line() +
  geom_point() + 
  scale_x_continuous(breaks = c(100,200,300,400,500,600,700,800,900,1000))
```

### Total time spent moving (Movement)
#### Creation of the dataset
I need to create a new dataset that excludes all turtles with no observation for total time spent moving
```{r}
cor.mov <- cor[complete.cases(cor$Movement),]

# deletion of the columns for handling reaction, shell emergence (and the binary version), and the time of initial movement (and the log transformed version)

drop <- c("Aggression", "Shell", "Bin.Shell", "Start", "log.Start")
cor.mov = cor.mov[,!(names(cor.mov) %in% drop)]
```

##### Pearson correlations between total time spent moving and land cover for each buffer distance  
```{r}
cor.pearson.mov <- rcorr(as.matrix(cor.mov[,3:53]), type="pearson")
```

##### Linearization of the correlation matrix
```{r}
table.cor.mov <- flattenCorrMatrix(cor.pearson.mov$r, cor.pearson.mov$P)
```

##### Save the table with the correlation in xlsx format
```{r}
write_xlsx(table.cor.mov, "C:/Users/sebas/Desktop/Masters Work/Masters Work/Stats/New Stats/Land Cover Correlation/Buffer Correlation/2022/Buffer Correlation Rankings/1000m Buffer Rankings/cor.mov.xlsx")
```

##### Upload the dataset that contain only the correlations with total time spent moving (delete all rows that don't have total time spent moving). 
```{r}
#I deleted the rows in Microsoft Excel
cor.mov.final<-read.csv("C:/Users/sebas/Desktop/Masters Work/Masters Work/Stats/New Stats/Land Cover Correlation/Buffer Correlation/2022/Buffer Correlation Rankings/1000m Buffer Rankings/cor.mov.csv")
```

##### Graphics illustrating the correlations between total time spent moving and landcover types at different buffer distances
```{r}
#Urban
ggplot(data=cor.mov.final, aes(x=buffer, y=cor.urban)) +
  geom_line() +
  geom_point() + 
  scale_x_continuous(breaks = c(100,200,300,400,500,600,700,800,900,1000))
#Forest/Vegetation
ggplot(data=cor.mov.final, aes(x=buffer, y=cor.for.veg)) +
  geom_line() +
  geom_point() + 
  scale_x_continuous(breaks = c(100,200,300,400,500,600,700,800,900,1000))
#Wetland
ggplot(data=cor.mov.final, aes(x=buffer, y=cor.wet)) +
  geom_line() +
  geom_point() + 
  scale_x_continuous(breaks = c(100,200,300,400,500,600,700,800,900,1000))
#Agriculture
ggplot(data=cor.mov.final, aes(x=buffer, y=cor.agri)) +
  geom_line() +
  geom_point() + 
  scale_x_continuous(breaks = c(100,200,300,400,500,600,700,800,900,1000))
#Water
ggplot(data=cor.mov.final, aes(x=buffer, y=cor.water)) +
  geom_line() +
  geom_point() + 
  scale_x_continuous(breaks = c(100,200,300,400,500,600,700,800,900,1000))
```